|

### 2023-04-25 manuscript/Chapter2-appendix1.Rmd
update appendix1 file

knitr::include_graphics(here::here("outputs", "04_outputs_figures", "appendix1_figureS1.png"))

@@

knitr::include_graphics(here::here("outputs", "04_outputs_figures", "appendix1_figureS2.png"))

@@

knitr::include_graphics(here::here("outputs", "04_outputs_figures", "appendix1_figureS3.png"))

>>>>

knitr::include_graphics(
  here::here(
    "outputs", "04_outputs_figures",
    "appendix1_figureS1.png"
  )
)

@@

knitr::include_graphics(
  here::here(
    "outputs", "04_outputs_figures",
    "appendix1_figureS2.png"
  )
)

@@

knitr::include_graphics(
  here::here(
    "outputs", "04_outputs_figures",
    "appendix1_figureS3.png"
  )
)
